---
title: "All spheroids comparison: time decision to touch"
output: html_document
date: "`r Sys.Date()`"
editor_options:
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This notebook uses data summary file `data_processed/data_summary/data_summary_all.csv`. The comparison is across the 3 spheroids with different aspect ratios nested under the TC/CT scenarios.



## Load libraries
```{r}
library(lme4)
library(lmerTest)
library(emmeans)
library(DHARMa)
library(tidyr)
library(dplyr)
```


## Set up path
```{r}
main_path = "~/code_git/porpoise_spheroid"
data_path = file.path(main_path, "data_processed/data_summary")
stat_path = file.path(main_path, "stat")
```

Create `stat` folder if it does not already exist:
```{r}
if (!dir.exists(stat_path)){
  dir.create(stat_path)
}
```


## Load data
```{r}
df = read.csv(
  file=paste(data_path, "data_summary_all.csv", sep="/")
)

# Get TC/CT position
df = df %>%
  separate(TARGET_ANGLE,  c("position"), sep=2, extra="drop", remove=FALSE) %>%
  filter(position=="TC" | position=="CT") %>%
  mutate(position=factor(position))
```


## Linear models

### Scan on sphere (ch0)
```{r}
lm_ch0 = lm(scan_ch0 ~ position + position:SPHEROID, data=df)
summary(lm_ch0)

glm_ch0_poisson = glm(scan_ch0 ~ position + position:SPHEROID, data=df, family=poisson)
summary(glm_ch0_poisson)

glm_ch0 = glm(scan_ch0 ~ position + position:SPHEROID, data=df, family=Gamma(link="log"))
summary(glm_ch0)
```

### Scan on sphere (ch1)
```{r}
lm_ch1 = lm(scan_ch1 ~ position + position:SPHEROID, data=df)
summary(lm_ch1)

glm_ch1_poisson = glm(scan_ch1 ~ position + position:SPHEROID, data=df, family=poisson)
summary(glm_ch1_poisson)

glm_ch1 = glm(scan_ch1 ~ position + position:SPHEROID, data=df, family=Gamma(link="log"))
summary(glm_ch1)
```



## Check the models

### Scan on sphere (ch0)

#### `lm`
```{r}
sim_ch0 = simulateResiduals(fittedModel=lm_ch0, n=250)
plot(sim_ch0, asFactor=FALSE)
sim_ch0_refit = simulateResiduals(fittedModel=lm_ch0, n=250, refit=TRUE)
lm_ch0_test_dispersion = testDispersion(sim_ch0_refit)
```

#### `glm` Poisson
```{r}
sim_ch0_poisson = simulateResiduals(fittedModel=glm_ch0_poisson, n=250)
plot(sim_ch0_poisson, asFactor=FALSE)
sim_ch0_poisson_refit = simulateResiduals(fittedModel=glm_ch0_poisson, n=250, refit=TRUE)
lm_ch0_test_dispersion = testDispersion(sim_ch0_poisson_refit)
```

#### `glm` Gamma
```{r}
sim_ch0_gamma = simulateResiduals(fittedModel=glm_ch0, n=250)
plot(sim_ch0_gamma, asFactor=FALSE)
sim_ch0_gamma_refit = simulateResiduals(fittedModel=glm_ch0, n=250, refit=TRUE)
glm_ch0_test_dispersion = testDispersion(sim_ch0_gamma_refit)
```

We can see that both the `lm` and `glm-Gamma` model fits the data well, so let’s use the simpler (`lm`) model going forward.


### Scan on spheroid (ch1)

#### `lm`
```{r}
sim_ch1 = simulateResiduals(fittedModel=lm_ch1, n=250)
plot(sim_ch1, asFactor=FALSE)
sim_ch1_refit = simulateResiduals(fittedModel=lm_ch1, n=250, refit=TRUE)
lm_ch1_test_dispersion = testDispersion(sim_ch1_refit)
```

#### `glm` Poisson
```{r}
sim_ch1_poisson = simulateResiduals(fittedModel=glm_ch1_poisson, n=250)
plot(sim_ch1_poisson, asFactor=FALSE)
sim_ch1_poisson_refit = simulateResiduals(fittedModel=glm_ch1_poisson, n=250, refit=TRUE)
lm_ch1_test_dispersion = testDispersion(sim_ch1_poisson_refit)
```

#### `glm` Gamma
```{r}
sim_ch1_gamma = simulateResiduals(fittedModel=glm_ch1, n=250)
plot(sim_ch1_gamma, asFactor=FALSE)
sim_ch1_gamma_refit = simulateResiduals(fittedModel=glm_ch1, n=250, refit=TRUE)
glm_ch1_test_dispersion = testDispersion(sim_ch1_gamma_refit)
```

Similar to the ch0 case, we can see that both the `lm` and `glm-Gamma` model fits the data well, so let’s use the simpler (`lm`) model going forward.




## Post hoc analysis

We can examine this more carefully with post-hoc analysis using `emmeans`.

### Scan on sphere (ch0)
```{r}
emm_lm_ch0 = emmeans(lm_ch0, ~position, type="response")
emm_lm_ch0

contrast(emm_lm_ch0, type="response")

emm_lm_ch0_2level = emmeans(lm_ch0, ~SPHEROID|position, type="response")
emm_lm_ch0_2level

contrast(emm_lm_ch0_2level, method="pairwise", type="response")
```

### Scan on sphere (ch1)
```{r}
emm_lm_ch1 = emmeans(lm_ch1, ~position, type="response")
emm_lm_ch1

contrast(emm_lm_ch1, type="response")

emm_lm_ch1_2level = emmeans(lm_ch1, ~SPHEROID|position, type="response")
emm_lm_ch1_2level

contrast(emm_lm_ch1_2level, method="pairwise", type="response")
```



## Session info
```{r}
sessionInfo()
```
