---
title: "All spheroids comparison: range to sphere/spheroid at decision"
output: html_document
date: "`r Sys.Date()`"
editor_options:
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This notebook uses data summary file `data_processed/data_summary/data_summary_all.csv`. The comparison is across the 3 spheroids with different aspect ratios nested under the TC/CT scenarios.



## Load libraries
```{r}
library(lme4)
library(lmerTest)
library(emmeans)
library(DHARMa)
library(tidyr)
library(dplyr)
```


## Set up path
```{r}
main_path = "~/code_git/porpoise_spheroid"
data_path = file.path(main_path, "data_processed/data_summary")
stat_path = file.path(main_path, "stat")
```

Create `stat` folder if it does not already exist:
```{r}
if (!dir.exists(stat_path)){
  dir.create(stat_path)
}
```


## Load data
```{r}
df = read.csv(
  file=paste(data_path, "data_summary_all.csv", sep="/")
)

# Get TC/CT position
df = df %>%
  separate(TARGET_ANGLE,  c("position"), sep=2, extra="drop", remove=FALSE) %>%
  filter(position=="TC" | position=="CT") %>%
  mutate(position=factor(position))
# df = df %>%
#   mutate(
#     SPHEROID=case_when(
#       SPHEROID=="L" ~  2.9,
#       SPHEROID=="M" ~ 1.3,
#       SPHEROID=="S" ~ 1.1,
#       .default = 0
#     )
#   ) %>%
#   mutate(SPHEROID=factor(SPHEROID))
```


## Linear models

### Range to sphere (target)
```{r}
lm_decision_ch0 = lm(range_decision_tar ~ position + position:SPHEROID, data=df)
summary(lm_decision_ch0)

glm_decision_ch0 = glm(range_decision_tar ~ position + position:SPHEROID, data=df, family=Gamma(link="log"))
summary(glm_decision_ch0)
```

### Range to spheroid (clutter)
```{r}
lm_decision_ch1 = lm(range_decision_clu ~ position + position:SPHEROID, data=df)
summary(lm_decision_ch1)

glm_decision_ch1 = glm(range_decision_clu ~ position + position:SPHEROID, data=df, family=Gamma(link="log"))
summary(glm_decision_ch1)
```




## Check the models

### Range to sphere (target)
#### `lm` model
```{r}
sim_decision_ch0 = simulateResiduals(fittedModel=lm_decision_ch0, n=250)
plot(sim_decision_ch0, asFactor=FALSE)
sim_decision_ch0_refit = simulateResiduals(fittedModel=lm_decision_ch0, n=250, refit=TRUE)
lm_decision_ch0_test_dispersion = testDispersion(sim_decision_ch0_refit)
```


#### `glm` model
```{r}
sim_decision_ch0_gamma = simulateResiduals(fittedModel=glm_decision_ch0, n=250)
plot(sim_decision_ch0_gamma, asFactor=FALSE)
sim_decision_ch0_gamma_refit = simulateResiduals(fittedModel=glm_decision_ch0, n=250, refit=TRUE)
glm_decision_ch0_test_dispersion = testDispersion(sim_decision_ch0_gamma_refit)
```

We can see that both models the data well, so let’s use the simpler (`lm`) model going forward.


### Range to spheroid (clutter)
#### `lm` model
```{r}
sim_decision_ch1 = simulateResiduals(fittedModel=lm_decision_ch1, n=250)
plot(sim_decision_ch1, asFactor=FALSE)
sim_decision_ch1_refit = simulateResiduals(fittedModel=lm_decision_ch1, n=250, refit=TRUE)
lm_decision_ch1_test_dispersion = testDispersion(sim_decision_ch1_refit)
```


#### `glm` model
```{r}
sim_decision_ch1_gamma = simulateResiduals(fittedModel=glm_decision_ch1, n=250)
plot(sim_decision_ch1_gamma, asFactor=FALSE)
sim_decision_ch1_gamma_refit = simulateResiduals(fittedModel=glm_decision_ch1, n=250, refit=TRUE)
glm_decision_ch1_test_dispersion = testDispersion(sim_decision_ch1_gamma_refit)
```

We can see that the `lm` model fits the data better, so let’s use it going forward.



## Post hoc analysis

We can examine this more carefully with post-hoc analysis using `emmeans`.

### Range to sphere (target)

```{r}
emm_lm = emmeans(lm_decision_ch0, ~position, type="response")
emm_lm

contrast(emm_lm, type="response")

emm_lm_2level = emmeans(lm_decision_ch0, ~SPHEROID|position, type="response")
emm_lm_2level

contrast(emm_lm_2level, method="pairwise", type="response")
```

### Range to spheroid (clutter)

```{r}
emm_lm = emmeans(lm_decision_ch1, ~position, type="response")
emm_lm

contrast(emm_lm, type="response")

emm_lm_2level = emmeans(lm_decision_ch1, ~SPHEROID|position, type="response")
emm_lm_2level

contrast(emm_lm_2level, method="pairwise", type="response")
```




## Session info
```{r}
sessionInfo()
```
