---
title: "All spheroids comparison: duration of last scan"
output: html_document
date: "`r Sys.Date()`"
editor_options:
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This notebook uses data summary file `data_processed/data_summary/data_summary_all.csv`. The comparison is across the 3 spheroids with different aspect ratios nested under the TC/CT scenarios.



## Load libraries
```{r}
library(lme4)
library(lmerTest)
library(emmeans)
library(DHARMa)
library(tidyr)
library(dplyr)
```


## Set up path
```{r}
main_path = "~/code_git/porpoise_spheroid"
data_path = file.path(main_path, "data_processed/data_summary")
stat_path = file.path(main_path, "stat")
```

Create `stat` folder if it does not already exist:
```{r}
if (!dir.exists(stat_path)){
  dir.create(stat_path)
}
```


## Load data
```{r}
df = read.csv(
  file=paste(data_path, "data_summary_all.csv", sep="/")
)

# Get TC/CT position
df = df %>%
  separate(TARGET_ANGLE,  c("position"), sep=2, extra="drop", remove=FALSE) %>%
  filter(position=="TC" | position=="CT") %>%
  mutate(position=factor(position))
```


## Linear models

### Duration of last scan
```{r}
lm_dura = lm(time_last_nonchosen ~ position + position:SPHEROID, data=df)
summary(lm_dura)

glm_dura = glm(time_last_nonchosen ~ position + position:SPHEROID, data=df, family=Gamma(link="log"))
summary(glm_dura)
```



## Check the models

### `lm` model
```{r}
sim_dura = simulateResiduals(fittedModel=lm_dura, n=250)
plot(sim_dura, asFactor=FALSE)
sim_dura_refit = simulateResiduals(fittedModel=lm_dura, n=250, refit=TRUE)
lm_dura_test_dispersion = testDispersion(sim_dura_refit)
```


### `glm` model
```{r}
sim_dura_gamma = simulateResiduals(fittedModel=glm_dura, n=250)
plot(sim_dura_gamma, asFactor=FALSE)
sim_dura_gamma_refit = simulateResiduals(fittedModel=glm_dura, n=250, refit=TRUE)
glm_dura_test_dispersion = testDispersion(sim_dura_gamma_refit)
```

We can see that the `glm` model fits the data better in terms of the quantile deviation, so let’s use the `glm` model going forward.



## Post hoc analysis

We can examine this more carefully with post-hoc analysis using `emmeans`.

```{r}
emm_lm = emmeans(glm_dura, ~position, type="response")
emm_lm

contrast(emm_lm, type="response")

emm_lm_2level = emmeans(glm_dura, ~SPHEROID|position, type="response")
emm_lm_2level

contrast(emm_lm_2level, method="pairwise", type="response")
```




## Session info
```{r}
sessionInfo()
```
