---
title: "AR=1.3 spheroid clusters comparison: time and range at decision"
output: html_document
date: "`r Sys.Date()`"
editor_options:
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This notebook uses data summary file `data_processed/data_summary/data_summary_cluster_only.csv`. The comparison is across 3 clusters (Straight, Curved-1, Curved-2) with each nested under the TC/CT scenarios.



## Load libraries
```{r}
library(lme4)
library(lmerTest)
library(emmeans)
library(DHARMa)
library(tidyr)
library(dplyr)
```


## Set up path
```{r}
main_path = "~/code_git/porpoise_spheroid"
data_path = file.path(main_path, "data_processed/data_summary")
stat_path = file.path(main_path, "stat")
```

Create `stat` folder if it does not already exist:
```{r}
if (!dir.exists(stat_path)){
  dir.create(stat_path)
}
```


## Load data
```{r}
df_cluster = read.csv(
  file=paste(data_path, "data_summary_cluster_only.csv", sep="/")
)

# Separate out fname_prefix into 3 columns DATE-SESSION-TRIAL
df_cluster = df_cluster %>%
  separate(fname_prefix, c("DATE","SESSION","TRIAL"), sep="_") %>%
  unite("DATE_SESSION", DATE:SESSION, remove=FALSE)

# Get cluster (Straight vs Curved) factor
df_cluster = df_cluster %>%
  separate(cluster, c("position","cluster"), sep="_", remove=FALSE)

# Convert SPHEROID column to factor for Cuzick test
df_cluster$SPHEROID = as.factor(df_cluster$SPHEROID)
df_cluster$position = as.factor(df_cluster$position)
df_cluster$cluster = as.factor(df_cluster$cluster)
```


## Linear models

### Time at decision to touch
```{r}
lm_time = lm(time_decision2touch ~ position + position:cluster, data=df_cluster)

lm_time_coeff = cbind(coef(summary(lm_time)), confint(lm_time))
lm_time_coeff

write.csv(lm_time_coeff, file.path(stat_path, "AR13_A_decision_time_coeff.csv"))
```

### Range to sphere (target)
```{r}
lm_range_target = lm(range_decision_tar ~ position + position:cluster, data=df_cluster)

lm_range_target_coeff = cbind(coef(summary(lm_range_target)), confint(lm_range_target))
lm_range_target_coeff

write.csv(lm_range_target_coeff, file.path(stat_path, "AR13_B1_decision_range_target_coeff.csv"))
```

### Range to spheroid (clutter)
```{r}
lm_range_clutter = lm(range_decision_clu ~ position + position:cluster, data=df_cluster)

lm_range_clutter_coeff = cbind(coef(summary(lm_range_clutter)), confint(lm_range_clutter))
lm_range_clutter_coeff

write.csv(lm_range_clutter_coeff, file.path(stat_path, "AR13_B2_decision_range_clutter_coeff.csv"))
```





## Post hoc analysis

### Time at decision to touch

#### Position (TC vs CT)
```{r}
# emmeans table
emm_time = emmeans(lm_time, ~position, type="response")
emm_time

write.csv(emm_time, file=file.path(stat_path, "AR13_A_decision_time_position_emmeans.csv"), row.names=FALSE)
```

```{r}
# contrast table with confidence level
s = summary(contrast(emm_time, method="revpairwise", type="response", level=0.95), infer=TRUE)
s
write.csv(s, file=file.path(stat_path, "AR13_A_decision_time_position_contrast.csv"), row.names=FALSE)
```

#### Cluster (Straight vs Curved-1 vs Curved-2)
```{r}
emm_time_2level = emmeans(lm_time, ~cluster|position, type="response")
emm_time_2level

write.csv(emm_time_2level, file=file.path(stat_path, "AR13_A_decision_time_cluster_emmeans.csv"), row.names=FALSE)
```

```{r}
# contrast table with confidence level
s = summary(contrast(emm_time_2level, method="pairwise", type="response", level=0.95), infer=TRUE)
s
write.csv(s, file=file.path(stat_path, "AR13_A_decision_time_cluster_contrast.csv"), row.names=FALSE)
```


### Range to sphere (target) at decision

#### Position (TC vs CT)
```{r}
# emmeans table
emm_range_target = emmeans(lm_range_target, ~position, type="response")
emm_range_target

write.csv(emm_range_target, file=file.path(stat_path, "AR13_B1_decision_range_target_position_emmeans.csv"), row.names=FALSE)
```

```{r}
# contrast table with confidence level
s = summary(contrast(emm_range_target, method="revpairwise", type="response", level=0.95), infer=TRUE)
s
write.csv(s, file=file.path(stat_path, "AR13_B1_decision_range_target_position_contrast.csv"), row.names=FALSE)
```

#### Cluster (Straight vs Curved-1 vs Curved-2)
```{r}
emm_range_target_2level = emmeans(lm_range_target, ~cluster|position, type="response")
emm_range_target_2level

write.csv(emm_range_target_2level, file=file.path(stat_path, "AR13_B1_decision_range_target_cluster_emmeans.csv"), row.names=FALSE)
```

```{r}
# contrast table with confidence level
s = summary(contrast(emm_range_target_2level, method="pairwise", type="response", level=0.95), infer=TRUE)
s
write.csv(s, file=file.path(stat_path, "AR13_B1_decision_range_target_cluster_contrast.csv"), row.names=FALSE)
```


### Range to spheroid (clutter) at decision

#### Position (TC vs CT)
```{r}
# emmeans table
emm_range_clutter = emmeans(lm_range_clutter, ~position, type="response")
emm_range_clutter

write.csv(emm_range_clutter, file=file.path(stat_path, "AR13_B2_decision_range_clutter_position_emmeans.csv"), row.names=FALSE)
```

```{r}
# contrast table with confidence level
s = summary(contrast(emm_range_clutter, method="revpairwise", type="response", level=0.95), infer=TRUE)
s
write.csv(s, file=file.path(stat_path, "AR13_B2_decision_range_clutter_position_contrast.csv"), row.names=FALSE)
```

#### Cluster (Straight vs Curved-1 vs Curved-2)
```{r}
emm_range_clutter_2level = emmeans(lm_range_clutter, ~cluster|position, type="response")
emm_range_clutter_2level

write.csv(emm_range_clutter_2level, file=file.path(stat_path, "AR13_B2_decision_range_clutter_cluster_emmeans.csv"), row.names=FALSE)
```

```{r}
# contrast table with confidence level
s = summary(contrast(emm_range_clutter_2level, method="pairwise", type="response", level=0.95), infer=TRUE)
s
write.csv(s, file=file.path(stat_path, "AR13_B2_decision_range_clutter_cluster_contrast.csv"), row.names=FALSE)
```





## Session info
```{r}
sessionInfo()
```
