---
title: "AR=1.3 spheroid clusters comparison: Combined number of scans"
output: html_document
date: "`r Sys.Date()`"
editor_options:
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This notebook uses data summary file `data_processed/data_summary/data_summary_cluster_only.csv`. The comparison is across 3 clusters (Straight, Curved-1, Curved-2) with each nested under the TC/CT scenarios.


## Load libraries
```{r}
library(lme4)
library(lmerTest)
library(emmeans)
library(tidyr)
library(dplyr)
```


## Set up path
```{r}
main_path = "~/code_git/porpoise_spheroid"
data_path = file.path(main_path, "data_processed/data_summary")
stat_path = file.path(main_path, "stat")
```

Create `stat` folder if it does not already exist:
```{r}
if (!dir.exists(stat_path)){
  dir.create(stat_path)
}
```


## Load data
```{r}
df_cluster = read.csv(
  file=paste(data_path, "data_summary_cluster_only.csv", sep="/")
)

# Separate out fname_prefix into 3 columns DATE-SESSION-TRIAL
df_cluster = df_cluster %>%
  separate(fname_prefix, c("DATE","SESSION","TRIAL"), sep="_") %>%
  unite("DATE_SESSION", DATE:SESSION, remove=FALSE)

# Get cluster (Straight vs Curved) factor
df_cluster = df_cluster %>%
  separate(cluster, c("position","cluster"), sep="_", remove=FALSE) %>%
  mutate(SPHEROID = factor(SPHEROID)) %>%
  mutate(position = factor(position, levels = c("TC", "CT"))) %>%
  mutate(cluster = factor(cluster, levels = c("Straight", "Curved-1", "Curved-2")))
```



## Linear models

### Combined number of scans
```{r}
lm = lm(scan_combined ~ position + position:cluster, data=df_cluster)

lm_coeff = cbind(coef(summary(lm)), confint(lm))
lm_coeff

write.csv(lm_coeff, file.path(stat_path, "AR13_scan_combined_coeff.csv"))
```




## Post hoc analysis

### Combined number of scans

#### Position (TC vs CT)
```{r}
# emmeans table
emm = emmeans(lm, ~position, type="response")
emm

write.csv(emm, file=file.path(stat_path, "AR13_scan_combined_position_emmeans.csv"), row.names=FALSE)
```

```{r}
# contrast table with confidence level
s = summary(contrast(emm, method="revpairwise", type="response", level=0.95), infer=TRUE)
s
write.csv(s, file=file.path(stat_path, "AR13_scan_combined_position_contrast.csv"), row.names=FALSE)
```

#### Cluster
```{r}
emm_2level = emmeans(lm, ~cluster|position, type="response")
emm_2level

write.csv(emm_2level, file=file.path(stat_path, "AR13_scan_combined_cluster_emmeans.csv"), row.names=FALSE)
```

```{r}
# contrast table with confidence level
s = summary(contrast(emm_2level, method="pairwise", type="response", level=0.95), infer=TRUE)
s
write.csv(s, file=file.path(stat_path, "AR13_scan_combined_cluster_contrast.csv"), row.names=FALSE)
```



## Session info
```{r}
sessionInfo()
```
