---
title: "All spheroids comparison: Decision time and range"
output: html_document
date: "`r Sys.Date()`"
editor_options:
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This notebook uses data summary file `data_processed/data_summary/data_summary_all.csv`. The comparison is across the 3 spheroids with different aspect ratios nested under the R+/L+ scenarios.



## Load libraries
```{r}
library(lme4)
library(lmerTest)
library(emmeans)
library(tidyr)
library(dplyr)
```


## Set up path
```{r}
main_path = "~/code_git/porpoise_spheroid"
data_path = file.path(main_path, "data_processed/data_summary")
stat_path = file.path(main_path, "stat")
```

Create `stat` folder if it does not already exist:
```{r}
if (!dir.exists(stat_path)){
  dir.create(stat_path)
}
```


## Load data
```{r}
df = read.csv(
  file=paste(data_path, "data_summary_all.csv", sep="/")
)

# Get R+/L+ position
df = df %>%
  separate(TARGET_ANGLE,  c("position"), sep=2, extra="drop", remove=FALSE) %>%
  filter(position=="TC" | position=="CT") %>%
  mutate(position=factor(position)) %>%
  filter(TRIAL_TO_INCLUDE=="Y") %>%
  filter(CHOICE == 1)

# Change L/M/S to AR=2.9/1.3/1.1
df = df %>%
  mutate(
    SPHEROID=case_when(
      SPHEROID=="L" ~  "AR=2.9",
      SPHEROID=="M" ~ "AR=1.3",
      SPHEROID=="S" ~ "AR=1.1",
      .default = ""
    )
  ) %>%
  mutate(SPHEROID=factor(SPHEROID, levels = c("AR=2.9", "AR=1.3", "AR=1.1"))) %>%
  mutate(position = factor(position, levels = c("TC", "CT"))) %>%
  mutate(
    position = case_when(
      position == "TC" ~ "R+",
      .default = "L+"
    )
  )
```


## Linear models

### Time at decision to touch
```{r}
lm_time = lm(time_decision2touch ~ position + position:SPHEROID, data=df)

lm_time_coeff = cbind(coef(summary(lm_time)), confint(lm_time))
lm_time_coeff

write.csv(lm_time_coeff, file.path(stat_path, "ARall_A_decision_time_coeff.csv"))
```

### Range to sphere (target)
```{r}
lm_range_target = lm(range_decision_tar ~ position + position:SPHEROID, data=df)

lm_range_target_coeff = cbind(coef(summary(lm_range_target)), confint(lm_range_target))
lm_range_target_coeff

write.csv(lm_range_target_coeff, file.path(stat_path, "ARall_B1_decision_range_target_coeff.csv"))
```

### Range to spheroid (clutter)
```{r}
lm_range_clutter = lm(range_decision_clu ~ position + position:SPHEROID, data=df)

lm_range_clutter_coeff = cbind(coef(summary(lm_range_clutter)), confint(lm_range_clutter))
lm_range_clutter_coeff

write.csv(lm_range_clutter_coeff, file.path(stat_path, "ARall_B1_decision_range_clutter_coeff.csv"))
```



## Post hoc analysis

### Time at decision to touch

#### Position (R+ vs L+)
```{r}
# emmeans table
emm_time = emmeans(lm_time, ~position, type="response")
emm_time

write.csv(emm_time, file=file.path(stat_path, "ARall_A_decision_time_position_emmeans.csv"), row.names=FALSE)
```

```{r}
# contrast table with confidence level
s = summary(contrast(emm_time, method="revpairwise", type="response", level=0.95), infer=TRUE)
s
write.csv(s, file=file.path(stat_path, "ARall_A_decision_time_position_contrast.csv"), row.names=FALSE)
```

#### Spheroid
```{r}
emm_time_2level = emmeans(lm_time, ~SPHEROID|position, type="response")
emm_time_2level

write.csv(emm_time_2level, file=file.path(stat_path, "ARall_A_decision_time_spheroid_emmeans.csv"), row.names=FALSE)
```

```{r}
# contrast table with confidence level
s = summary(contrast(emm_time_2level, method="pairwise", type="response", level=0.95), infer=TRUE)
s
write.csv(s, file=file.path(stat_path, "ARall_A_decision_time_spheroid_contrast.csv"), row.names=FALSE)
```


### Range to sphere (target) at decision

#### Position (R+ vs L+)
```{r}
# emmeans table
emm_range_target = emmeans(lm_range_target, ~position, type="response")
emm_range_target

write.csv(emm_range_target, file=file.path(stat_path, "ARall_B1_decision_range_target_position_emmeans.csv"), row.names=FALSE)
```

```{r}
# contrast table with confidence level
s = summary(contrast(emm_range_target, method="revpairwise", type="response", level=0.95), infer=TRUE)
s
write.csv(s, file=file.path(stat_path, "ARall_B1_decision_range_target_position_contrast.csv"), row.names=FALSE)
```

#### Spheroid
```{r}
emm_range_target_2level = emmeans(lm_range_target, ~SPHEROID|position, type="response")
emm_range_target_2level

write.csv(emm_range_target_2level, file=file.path(stat_path, "ARall_B1_decision_range_target_spheroid_emmeans.csv"), row.names=FALSE)
```

```{r}
# contrast table with confidence level
s = summary(contrast(emm_range_target_2level, method="pairwise", type="response", level=0.95), infer=TRUE)
s
write.csv(s, file=file.path(stat_path, "ARall_B1_decision_range_target_spheroid_contrast.csv"), row.names=FALSE)
```


### Range to spheroid (clutter) at decision

#### Position (R+ vs L+)
```{r}
# emmeans table
emm_range_clutter = emmeans(lm_range_clutter, ~position, type="response")
emm_range_clutter

write.csv(emm_range_clutter, file=file.path(stat_path, "ARall_B2_decision_range_clutter_position_emmeans.csv"), row.names=FALSE)
```

```{r}
# contrast table with confidence level
s = summary(contrast(emm_range_clutter, method="revpairwise", type="response", level=0.95), infer=TRUE)
s
write.csv(s, file=file.path(stat_path, "ARall_B2_decision_range_clutter_position_contrast.csv"), row.names=FALSE)
```

#### Spheroid
```{r}
emm_range_clutter_2level = emmeans(lm_range_clutter, ~SPHEROID|position, type="response")
emm_range_clutter_2level

write.csv(emm_range_clutter_2level, file=file.path(stat_path, "ARall_B2_decision_range_clutter_spheroid_emmeans.csv"), row.names=FALSE)
```

```{r}
# contrast table with confidence level
s = summary(contrast(emm_range_clutter_2level, method="pairwise", type="response", level=0.95), infer=TRUE)
s
write.csv(s, file=file.path(stat_path, "ARall_B2_decision_range_clutter_spheroid_contrast.csv"), row.names=FALSE)
```




## Session info
```{r}
sessionInfo()
```
