---
title: "All spheroids comparison: Combined number of scans"
output: html_document
date: "`r Sys.Date()`"
editor_options:
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This notebook uses data summary file `data_processed/data_summary/data_summary_all.csv`. The comparison is across the 3 spheroids with different aspect ratios nested under the R+/L+ scenarios.


## Load libraries
```{r}
library(lme4)
library(lmerTest)
library(emmeans)
library(tidyr)
library(dplyr)
```


## Set up path
```{r}
main_path = "~/code_git/porpoise_spheroid"
data_path = file.path(main_path, "data_processed/data_summary")
stat_path = file.path(main_path, "stat")
```

Create `stat` folder if it does not already exist:
```{r}
if (!dir.exists(stat_path)){
  dir.create(stat_path)
}
```


## Load data
```{r}
df = read.csv(
  file=paste(data_path, "data_summary_all.csv", sep="/")
)

# Get R+/L+ position
df = df %>%
  separate(TARGET_ANGLE,  c("position"), sep=2, extra="drop", remove=FALSE) %>%
  filter(position=="TC" | position=="CT") %>%
  mutate(position=factor(position)) %>%
  filter(TRIAL_TO_INCLUDE=="Y") %>%
  filter(CHOICE == 1)


# Change L/M/S to AR=2.9/1.3/1.1
df = df %>%
  mutate(
    SPHEROID=case_when(
      SPHEROID=="L" ~  "AR=2.9",
      SPHEROID=="M" ~ "AR=1.3",
      SPHEROID=="S" ~ "AR=1.1",
      .default = ""
    )
  ) %>%
  mutate(SPHEROID=factor(SPHEROID, levels = c("AR=2.9", "AR=1.3", "AR=1.1"))) %>%
  mutate(position = factor(position, levels = c("TC", "CT"))) %>%
  mutate(
    position = case_when(
      position == "TC" ~ "R+",
      .default = "L+"
    )
  )
```


## Linear models

### Combined number of scans
```{r}
lm = lm(scan_combined ~ position + position:SPHEROID, data=df)

lm_coeff = cbind(coef(summary(lm)), confint(lm))
lm_coeff

write.csv(lm_coeff, file.path(stat_path, "ARall_scan_combined_coeff.csv"))
```




## Post hoc analysis

### Combined number of scans

#### Position (R+ vs L+)
```{r}
# emmeans table
emm = emmeans(lm, ~position, type="response")
emm

write.csv(emm, file=file.path(stat_path, "ARall_scan_combined_position_emmeans.csv"), row.names=FALSE)
```

```{r}
# contrast table with confidence level
s = summary(contrast(emm, method="revpairwise", type="response", level=0.95), infer=TRUE)
s
write.csv(s, file=file.path(stat_path, "ARall_scan_combined_position_contrast.csv"), row.names=FALSE)
```

#### Spheroid
```{r}
emm_2level = emmeans(lm, ~SPHEROID|position, type="response")
emm_2level

write.csv(emm_2level, file=file.path(stat_path, "ARall_scan_combined_spheroid_emmeans.csv"), row.names=FALSE)
```

```{r}
# contrast table with confidence level
s = summary(contrast(emm_2level, method="pairwise", type="response", level=0.95), infer=TRUE)
s
write.csv(s, file=file.path(stat_path, "ARall_scan_combined_spheroid_contrast.csv"), row.names=FALSE)
```



## Session info
```{r}
sessionInfo()
```
