---
title: "All spheroids comparison: Number of scans to sphere/spheroid"
output: html_document
date: "`r Sys.Date()`"
editor_options:
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This notebook uses data summary file `data_processed/data_summary/data_summary_all.csv`. The comparison is across the 3 spheroids with different aspect ratios nested under the TC/CT scenarios.


## Load libraries
```{r}
library(lme4)
library(lmerTest)
library(emmeans)
library(tidyr)
library(dplyr)
```


## Set up path
```{r}
main_path = "~/code_git/porpoise_spheroid"
data_path = file.path(main_path, "data_processed/data_summary")
stat_path = file.path(main_path, "stat")
```

Create `stat` folder if it does not already exist:
```{r}
if (!dir.exists(stat_path)){
  dir.create(stat_path)
}
```


## Load data
```{r}
df = read.csv(
  file=paste(data_path, "data_summary_all.csv", sep="/")
)

# Get TC/CT position
df = df %>%
  separate(TARGET_ANGLE,  c("position"), sep=2, extra="drop", remove=FALSE) %>%
  filter(position=="TC" | position=="CT") %>%
  mutate(position=factor(position)) %>%
  filter(TRIAL_TO_INCLUDE=="Y")


# Change L/M/S to AR=2.9/1.3/1.1
df = df %>%
  mutate(
    SPHEROID=case_when(
      SPHEROID=="L" ~  "AR=2.9",
      SPHEROID=="M" ~ "AR=1.3",
      SPHEROID=="S" ~ "AR=1.1",
      .default = ""
    )
  ) %>%
  mutate(SPHEROID=factor(SPHEROID))
```


## Linear models

### Scan on sphere (ch0)
```{r}
lm_ch0 = lm(scan_ch0 ~ position + position:SPHEROID, data=df)

lm_ch0_coeff = cbind(coef(summary(lm_ch0)), confint(lm_ch0))
lm_ch0_coeff

write.csv(lm_ch0_coeff, file.path(stat_path, "ARall_E_scan_ch0_coeff.csv"))
```

### Scan on spheroid (ch1)
```{r}
lm_ch1 = lm(scan_ch1 ~ position + position:SPHEROID, data=df)

lm_ch1_coeff = cbind(coef(summary(lm_ch1)), confint(lm_ch1))
lm_ch1_coeff

write.csv(lm_ch1_coeff, file.path(stat_path, "ARall_F_scan_ch1_coeff.csv"))
```




## Post hoc analysis

### Scan on sphere (ch0)

#### Position (TC vs CT)
```{r}
# emmeans table
emm_ch0 = emmeans(lm_ch0, ~position, type="response")
emm_ch0

write.csv(emm_ch0, file=file.path(stat_path, "ARall_E_scan_ch0_position_emmeans.csv"), row.names=FALSE)
```

```{r}
# contrast table with confidence level
s = summary(contrast(emm_ch0, method="revpairwise", type="response", level=0.95), infer=TRUE)
s
write.csv(s, file=file.path(stat_path, "ARall_E_scan_ch0_position_contrast.csv"), row.names=FALSE)
```

#### Spheroid
```{r}
emm_ch0_2level = emmeans(lm_ch0, ~SPHEROID|position, type="response")
emm_ch0_2level

write.csv(emm_ch0_2level, file=file.path(stat_path, "ARall_E_scan_ch0_spheroid_emmeans.csv"), row.names=FALSE)
```

```{r}
# contrast table with confidence level
s = summary(contrast(emm_ch0_2level, method="pairwise", type="response", level=0.95), infer=TRUE)
s
write.csv(s, file=file.path(stat_path, "ARall_E_scan_ch0_spheroid_contrast.csv"), row.names=FALSE)
```


### Scan on spheroid (ch1)

#### Position (TC vs CT)
```{r}
# emmeans table
emm_ch1 = emmeans(lm_ch1, ~position, type="response")
emm_ch1

write.csv(emm_ch1, file=file.path(stat_path, "ARall_F_scan_ch1_position_emmeans.csv"), row.names=FALSE)
```

```{r}
# contrast table with confidence level
s = summary(contrast(emm_ch1, method="revpairwise", type="response", level=0.95), infer=TRUE)
s
write.csv(s, file=file.path(stat_path, "ARall_F_scan_ch1_position_contrast.csv"), row.names=FALSE)
```

#### Spheroid
```{r}
emm_ch1_2level = emmeans(lm_ch1, ~SPHEROID|position, type="response")
emm_ch1_2level

write.csv(emm_ch1_2level, file=file.path(stat_path, "ARall_F_scan_ch1_spheroid_emmeans.csv"), row.names=FALSE)
```

```{r}
# contrast table with confidence level
s = summary(contrast(emm_ch1_2level, method="pairwise", type="response", level=0.95), infer=TRUE)
s
write.csv(s, file=file.path(stat_path, "ARall_F_scan_ch1_spheroid_contrast.csv"), row.names=FALSE)
```



## Session info
```{r}
sessionInfo()
```
